Shaping strategy in core and flake industry：Standardized manufacturing of QSY (North China) faceted spheroids

### 2025-06-03 analysis/paper/paper.qmd
updates

We applied diacritical analysis to reconstruct the reduction sequence based on superimposition relationships among scars on spheroids. This method enables the identification of scars order, allowing us to figure out the organization of removals. All spheroids, polyhedron and multifacial cores are included in the analysis to assess whether removals organization differs systematically within these groups.

@@

To further investigate technological strategies, we incorporated orientation statistics as a complementary approach. This method derives from fabric analysis originally used in sedimentology and has since been adapted to study the arrangement of flake scars on lithic artifacts. We followed the protocol developed by Sam Lin, extracting scar vectors from each core and calculating eigenvalues to derive the isotropic ratio and elongation ratio, these steps are finished in Geomagic Wrap, Rhino8 and R.

>>>>

We applied diacritical analysis to reconstruct the reduction sequence based on superimposition relationships among scars on spheroids [@Titton2020; @Cabanès2024]. This method enables the identification of scars order, allowing us to figure out the organization of removals. All spheroids, polyhedron and multifacial cores are included in the analysis to assess whether removals organization differs systematically within these groups.

@@

To further investigate technological strategies, we incorporated orientation statistics as a complementary approach. This method derives from fabric analysis originally used in sedimentology and has since been adapted to study the arrangement of flake scars on lithic artifacts. We followed the protocol developed by Sam Lin [@Lin2024], extracting scar vectors from each core and calculating eigenvalues to derive the isotropic ratio and elongation ratio, these steps are finished in Geomagic Wrap, Rhino8 and R.
